Smoothing seismicity techniques applied to seismic sources characterization and probabilistic seismic hazard analysis in Brazil

### 2015-01-16 manuscript.tex
improove data description and figures layout

@@

@@

\subsection{Catalog overview}

@@

@@

blsbalba

\subsection{Catalog completeness}

blsbalba

@@

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\footnotesize(a)
		& 
		\footnotesize(b)
		\\		
		\includegraphics[width=0.45\textwidth]{placeholder} &
		\includegraphics[width=0.45\textwidth]{placeholder}
		\end{tabular}
	\end{table}
	\caption{This tabled figure shows the first (a) image and the 2nd one (b). Even with the same bla ba.}
	\label{placeholder}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.33\textwidth} 
						 p{0.33\textwidth} 
						 p{0.33\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\				
		\includegraphics[width=0.33\textwidth]{z_img_pga_frankel} &
		\includegraphics[width=0.33\textwidth]{z_img_pga_woo} &
		\includegraphics[width=0.33\textwidth]{z_img_pga_helmstetter}
		\end{tabular}
	\end{table}
	\caption{This tabled figure shows the first (a) image and the 2nd one (b). Even with the same bla ba.}
	\label{placeholder2}
	\end{center}
\end{figure}

% =========
% data
% =========

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_time_mag_count_br_1960}
	\caption{Magnitude count by year.}
	\label{fig_time_mag_count}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_decluster_br}
	\caption{Catalog declustering.}
	\label{fig_decluster}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_occurrence}
	\caption{Annual earthquake recurrence.}
	\label{fig_occurrence}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_a_frankel_br}
	\caption{Smoothed seismicity: Frankel's method.}
	\label{fig_a_frankel}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_a_woo}
	\caption{Smoothed seismicity: Woo's method.}
	\label{fig_a_woo}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_a_helmstetter}
	\caption{Smoothed seismicity: Helmstetter's method.}
	\label{fig_a_helmstetter}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_pga_gshap}
	\caption{GSHAP results: PGA (poe 10\%/50y)}
	\label{fig_pga_gshap}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_pga_frankel}
	\caption{Frankel's results: PGA (poe 10\%/50y)}
	\label{fig_pga_frankel}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_pga_woo}
	\caption{Woo's results: PGA (poe 10\%/50y)}
	\label{fig_pga_woo}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_pga_helmstetter}
	\caption{Helmstetter's results: PGA (poe 10\%/50y)}
	\label{fig_pga_helmstetter}
\end{figure}

>>>>

\subsection{Hypocenters}

@@

\subsection{Magnitudes}

@@

\subsection{Catalog check}

@@

The annual earthquake records since 1900 on the catalog is on the figure \ref{fig_records} where is evident the seismicity increase arround 1986 and 1998 (???) derived by João Câmara [REFERENCE] and BEBEDOURO, SOBRAL?!? activity. Also is possible to note the increasing number of records after 1960 due the operation of global, regional and local stations since that.

@@

To preserve the Poisson assumption about the independece of the events on the catalog, it was submited to some decluster algorithms and the results is shown on the figure \ref{fig_decluster}a.

The window-method \citep{gardner_1974} was tested with three different windows: \citet{gardner_1974}, \citet{uhrhammer_1986} and Gr\"uental \citep{marsan_david_2012}. In addition the algorithm (AFTERAN) proposed by \citet{musson_1999} was also tested using Gr\"uental distance window.

In the case of this catalog the methods did not presented strong differences at the final results (fig. \ref{fig_decluster}a) and the final choose of Gardner-Knopof/Uhrhammer was based on criteria to maximize the number of events to be analysed.

The map on figure \ref{fig_decluster}b locate all clusters in the catalog. It is an \emph{a-priori} evidence of regions in Brazil where in some time, earthquakes occur sistematically.

\subsection{Frequency-magnitude distribution}

Figure \ref{fig_occurrence} presents the magnitude and frequency distribution.
A general $b=1$ fit is also plotted, and the completeness magnitude on the incremental distribution is about 3.0.

\subsection{Catalogue completeness}

The Brazilian seismicity data completeness has evident time and space dependence. The number of stations and their accuracy increased in the time, and the spatial occupation respects the population density coverage concentrated in the east coast in almost cases with exception only in the central part of the country by the Brasilia Seismic Station (REFERENCE).

The spatial completeness dependence was not considered on this work. History of almost regional stations was not easy available and blocks methodologies, e.g. \citet{mignan_2011} work.

Time dependence was defined by expert criteria and it is shown on the figure

@@

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
% 		\footnotesize(a)
% 		& 
% 		\footnotesize(b)
% 		\\		
% 		\includegraphics[width=0.45\textwidth]{placeholder} &
% 		\includegraphics[width=0.45\textwidth]{placeholder}
% 		\end{tabular}
% 	\end{table}
% 	\caption{This tabled figure shows the first (a) image and the 2nd one (b). Even with the same bla ba.}
% 	\label{placeholder}
% 	\end{center}
% \end{figure}

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.33\textwidth} 
% 						 p{0.33\textwidth} 
% 						 p{0.33\textwidth} }
% 		\footnotesize(a) &
% 		\footnotesize(b) &
% 		\footnotesize(c)
% 		\\				
% 		\includegraphics[width=0.33\textwidth]{z_img_pga_frankel} &
% 		\includegraphics[width=0.33\textwidth]{z_img_pga_woo} &
% 		\includegraphics[width=0.33\textwidth]{z_img_pga_helmstetter}
% 		\end{tabular}
% 	\end{table}
% 	\caption{This tabled figure shows the first (a) image and the 2nd one (b). Even with the same bla ba.}
% 	\label{placeholder2}
% 	\end{center}
% \end{figure}

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\begin{tabular}{ c c }
		\footnotesize(a)
		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_rate}
		\\		
		\footnotesize(b) 
		& \includegraphics[width=0.40\textwidth]{z_img_time_mag_count_br_1960}
		\end{tabular}
	\end{table}
	\caption{Earthquakes by year (a) and discriminated by magnitude (b).}
	\label{fig_records}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\begin{tabular}{ c c }
		\footnotesize(a)
		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_decluster}
		\\		
		\footnotesize(b) 
		& \includegraphics[width=0.40\textwidth]{z_img_hmtk_bsb2013_pp_decluster}
		\end{tabular}
	\end{table}
	\caption{Decluster evaluation (a) and the clusters map (b).}
	\label{fig_decluster}
	\end{center}
\end{figure}

\begin{figure}
	\includegraphics[width=1.0\linewidth]{z_img_hmtk_bsb2014_11_completeness}
	\caption{Annual earthquake recurrence.}
	\label{fig_occurrence}
\end{figure}

@@

@@

@@

% =========
% Smoothed Rates
% =========

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.33\textwidth} 
						 p{0.34\textwidth} 
						 p{0.33\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\				
		\includegraphics[height=5cm]{z_img_a_frankel_br}  &
		\includegraphics[height=5cm]{z_img_a_woo} &
		\includegraphics[height=5cm]{z_img_a_helmstetter}
		\end{tabular}
	\end{table}
	\caption{Smoothed rates comparission: (a) shows \citet{frankel_1995} method smoothed rate results, (b) and (c) represent rates smoothed by \citet{woo_1996} and \citet{helmstetter_2012} methods respectly.}
	\label{fig_rates}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.33\textwidth} 
						 p{0.34\textwidth} 
						 p{0.33\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\				
		\includegraphics[height=5cm]{z_img_pga_frankel}  &
		\includegraphics[height=5cm]{z_img_pga_woo} &
		\includegraphics[height=5cm]{z_img_pga_helmstetter}
		\end{tabular}
	\end{table}
	\caption{PGA (poe 10\%/50y) comparission for (a) \citet{frankel_1995}, (b) \citet{woo_1996} and (c) \citet{helmstetter_2012} methods.}
	\label{fig_pga}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\footnotesize(a)
		& 
		\footnotesize(b)
		\\		
		\includegraphics[width=0.45\textwidth]{z_img_pga_gshap} &
		\includegraphics[width=0.45\textwidth]{z_img_pga_helmstetter}
		\end{tabular}
	\end{table}
	\caption{Previous available Brazillian PSHA from (a) GSHAP project and the PSHA proposed by this work (b). }
	\label{placeholder}
	\end{center}
\end{figure}
